The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-13 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to paper
Changed some examples

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

i17 : fpt(f, DepthOfSearch => 3, Attempts => 2)

        3   7
o17 = {--, ---}
       62  125

o17 : List

i18 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always*
      improve the estimate

        1   4
o18 = {--, --}
       20  75

o18 : List

i19 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator)
      -- the exact answer, after a change of strategy

       1
o19 = --
      19

o19 : QQ
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i23 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;

i24 : numeric fpt(f, DepthOfSearch => 3)

o24 = {.153226, .158333}

i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
      -- FinalAttempt improves the estimate slightly

o25 = {.153461, .158333}

o25 : List
\end{MyVerbatim}
}
\bigskip

% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
% numeric fpt(f, DepthOfSearch => 3)
% numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true) -- FinalAttempt improves the estimate slightly

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i26 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;

i27 : timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)

o27 = {.153461, .158333}
      -- 1.37902 seconds

o27 : Time

i28 : timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better
      answer in less time

o28 = {.153333, .158333}
      -- .614248 seconds

o28 : Time

i29 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
      time

       98
o29 = ---
      625
      -- .297493 seconds

o29 : Time
\end{MyVerbatim}
}
\bigskip

% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
% timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
% timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better answer in less time
% timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less time

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i30 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;

i31 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)

@@

ν has been computed: ν = ν(3,f) = 9 ...

fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [9/124,2/25] ...

@@

guessFPT narrowed the interval down to (3/40,2/25) ...

@@

First F-signature computed: s(f,(ν-1)/p^e) = 456/15625 ...

Second F-signature computed: s(f,ν/p^e) = 64/15625 ...

Computed F-signature secant line intercept: 449/6125 ...

F-signature computation failed to find an improved lower bound ...

@@

fpt lies in the interval (3/40,2/25).

        3   2
o31 = {--, --}
       40  25

o31 : List
\end{MyVerbatim}
}
\bigskip

>>>>

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

i13 : fpt(f, DepthOfSearch => 3, Attempts => 4)

        1   4
o13 = {--, --}
       20  75

o13 : List

i14 : fpt(f, DepthOfSearch => 3, Attempts => 6)

        13   4
o14 = {---, --}
       250  75

i15 : fpt(f, DepthOfSearch => 3, Attempts => 8)

       1
o15 = --
      19

o15 : QQ
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i2 : f = 2*x^10*y^8+x^4*y^7-2*x^3*y^8;

i3 : numeric fpt(f, DepthOfSearch => 3)

o3 = {.14, .144}

o3 : List

i4 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- FinalAttempt improves the estimate slightly

o4 = {.142067, .144}

o4 : List
\end{MyVerbatim}
}
\bigskip

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i35 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- used 0.684759 seconds

o35 = {.142067, .144}

o35 : List

i36 : time fpt(f, DepthOfSearch => 3, Attempts => 7) 
     -- used 0.405148 seconds

      1
o36 = -
      7

o36 : QQ

i37 : time fpt(f, DepthOfSearch => 4) 
     -- used 0.365025 seconds

      1
o37 = -
      7

o37 : QQ
\end{MyVerbatim}
}
\bigskip

@@

\pedro[inline]{
   Maybe the example below could be omitted, to shorten the paper.
   I think that just telling the reader that the interval is printed when Verbose is activated is enough.
}

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i39 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)

@@

ν has been computed: ν = ν(3,f) = 17 ...

fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...

@@

guessFPT narrowed the interval down to (7/50,18/125) ...

@@

First F-signature computed: s(f,(ν-1)/p^e) = 793/15625 ...

Second F-signature computed: s(f,ν/p^e) = 342/15625 ...

Computed F-signature secant line intercept: 8009/56375 ...

F-signature intercept is an improved lower bound;
Using F-regularity to check if it is the fpt ...

The new lower bound is not the fpt ...

@@

fpt lies in the interval (8009/56375,18/125).

        8009   18
o39 = {-----, ---}
       56375  125

o39 : List
\end{MyVerbatim}
}
\bigskip
